Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-31 journal/article.tex
T: External consultants

Even if any activities aiming for transformation can be considered as
investments in themselves, the transformation process included specific
investments in some tangible entities. These investments were focused on better
enabling agile software development, and highlight the concerns that
organizations had when implementing an agile model. Typical investments were new
management tools, improvements in testing environments, and updating of the
physical working spaces. Table \ref{table:transformation_investments} summarizes
common types of investments.

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.42\textwidth}
                     >{\raggedright\arraybackslash}p{0.50\textwidth} }
        Investment for transformation      &  Described in  \\
        \midrule
        Agile project management tools  &
                P10, P11, P14, P16, P17, P26, P33,
                P41, P43, P44, P45, P48, P50 \\
        Continuous builds and testing  &
                P5, P11, P16, P17, P25, P27, P34, P39, P42, P50 \\
        Proprietary agile material or documentation   & 
                P1, P2, P8, P14, P16, P23, P26, P29, P32, P45  \\
        Refurbishing work areas and other spaces   &
                P6, P22, P35, P36, P38, P42, P46, P48 \\
        \bottomrule
    \end{tabular}
    \caption{Summary of investments aiming to make agile methods perform better}
    \label{table:transformation_investments}
\end{table}

>>>>

Even if any activities aiming for transformation can be considered as
investments in themselves, the transformation process included some specific
tangible investments. These investments were focused on better enabling agile
software development, and highlight the concerns that organizations had when
implementing an agile model. Typical investments were bringing in external help,
new management tools, improvements in testing environments, and updating of the
physical working spaces. Table \ref{table:transformation_investments} summarizes
common types of investments.

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.35\textwidth}
                     >{\raggedright\arraybackslash}p{0.57\textwidth} }
        Investment for transformation      &  Described in  \\
        \midrule
        Using external consultants  &
                P5-P9, P16-P21, P23 P25, P27, P29-P31,
                P34, P35, P37-P41, P44, P46, P47, P50, P51  \\  % 29
        Agile project management tools  &
                P10, P11, P14, P16, P17, P26, P33,
                P41, P43, P44, P45, P48, P50 \\
        Continuous builds and testing  &
                P5, P11, P16, P17, P25, P27, P34, P39, P42, P50 \\
        Proprietary agile material or documentation   & 
                P1, P2, P8, P14, P16, P23, P26, P29, P32, P45  \\
        Refurbishing work areas and other spaces   &
                P6, P22, P35, P36, P38, P42, P46, P48 \\
        \bottomrule
    \end{tabular}
    \caption{Summary of investments aiming to make agile methods perform better}
    \label{table:transformation_investments}
\end{table}

% External consultants

It was very typical that external help was brought in to help with the
transformation.
External consultants were employed especially at the start of the
transformation. At the time it was realized that the way of working should be
changed a consultant was often hired to assess the current state and give a
recommendation on how to proceed [P16, P20, P41, P43, P41, P44, P51].
In the beginning external consultants were used to ignite interest in agile
methods, and provide initial education [P7, P9, P27, P30, P43].
It was recommended to bring in extenal help as early as possible, when the
internal agile expertise is lacking and before transformation challenges appear
[P6, P16, P30].

When the transformation was getting on its way, agile consultants were typically
leading training sessions, arranging agile workshops, and coaching teams.
In some cases consultants helped specifically with scaling up the use of agile
beyond single teams [P31, P34].
Consultants were used mostly in the first stages of the transformation.
The need for external consultants reduced over time, and their tasks were
transfered to internal positions [P29, P47].
It was described that as the agile journey progressed, external consultants were
invited every now and then to bring in fresh ideas to the organization [P6].

External consultants were regarded to bring in critical assistance in
transforming the organization [P6, P16, P17]. Qualities in external consultants
that organizations looked for was leveraging their experience to bring more
speed to development and agile adoption [P17, P27, P34, P35, P40], and to bring
in agile skill when only little existed in-house [P27, P47]. It was considered
beneficial having experts with previous experience of transforming organizations
[P16, P27].
Still one important aspect in using consultants was that people were more
comfortable when the advice was given by impartial persons external to the
organization [P16, P29, P44].

% In one case the teams were sceptical of having external consultants embedded
% in temas [P27].
